\documentclass[10pt,a4paper,twoside]{article}
\usepackage{pstricks}
\usepackage{fancybox}
\usepackage{amsfonts}
% \usepackage{minitoc}
% \setcounter{minitocdepth}{2}
\usepackage[bookmarks=true, 
            bookmarksnumbered=true, 
            bookmarksopen=false, 
            plainpages=false,
            pdfpagelabels,
            colorlinks, 
            citecolor=red,
            linkcolor=blue]{hyperref}
\usepackage{ifthen}
\usepackage{graphicx}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}

%\newboolean{mtc}
%\setboolean{mtc}{true}

\pdfoutput=1
\relax
\pdfcompresslevel=0             %-- 0 = none, 9 = best
\pdfinfo{                       %-- Info dictionary of PDF output  /Author (Alfredo Buttari)
  /Title (Parallel Sparse BLAS V. 3.0-beta)
  /Subject (Parallel Sparse Basic Linear Algebra Subroutines)
  /Keywords (Computer Science Linear Algebra Fluid Dynamics Parallel Linux MPI PSBLAS Iterative Solvers Preconditioners)
  /Creator (pdfLaTeX)
  /Producer ($Id$)
}
\pdfcatalog{          %-- Catalog dictionary of PDF output.
  /URI (http://ce.uniroma2.it/psblas)
} 

\newcounter{subroutine}[subsection]
\newcounter{example}[subroutine]
\makeatletter
\def\subroutine{\@ifstar{\@subroutine}{\clearpage\@subroutine}}%
\def\@subroutine#1#2{%
\stepcounter{subroutine}%
      \section*{\flushleft #1---#2 \endflushleft}%
      \addcontentsline{toc}{subsection}{#1}%
      \markright{#1}}%
\newcommand{\subsubroutine}[2]{%
\stepcounter{subroutine}%
      \subsection*{\flushleft #1---#2 \endflushleft}%
      \addcontentsline{toc}{subsubsection}{#1}%
      \markright{#1}}%
\newcommand{\examplename}{Example}
\newcommand{\syntaxname}{Syntax}
\def\syntax{\@ifstar{\@ssyntax}{\@syntax}}%
\def\@syntax{\nobreak\section*{\syntaxname}%
     \@ssyntax}%
\def\@ssyntax#1#2{%
  \nobreak
   \setbox\@tempboxa\hbox{#1\ {\em $($#2$)$}}%
   \ifdim \wd\@tempboxa >\hsize
        \setbox\@tempboxa\hbox{\em $($#2$)$}
	\ifdim\wd\@tempboxa >\hsize
          \flushright#1\ \em$($#2$)$\endflushright%
	\else
         \hbox to\hsize{#1\hfil}%
         \hbox to\hsize{\hfil\box\@tempboxa}%
        \fi
     \else
       \hbox to\hsize{\hfil\box\@tempboxa\hfil}%
   \fi\par\vskip\baselineskip}
\makeatother
\newcommand{\example}{\stepcounter{example}%
\section*{\examplename~\theexample}}

\newcommand{\precdata}{\hyperlink{precdata}{{\tt psb\_prec\_type}}}
\newcommand{\descdata}{\hyperlink{descdata}{{\tt psb\_desc\_type}}}
\newcommand{\spdata}{\hyperlink{spdata}{{\tt psb\_spmat\_type}}}

\begin{document}

\pdfbookmark{PSBLAS-v3.0-beta User's Guide}{title}

\newlength{\centeroffset}
\setlength{\centeroffset}{-0.5\oddsidemargin}
\addtolength{\centeroffset}{0.5\evensidemargin}
%\addtolength{\textwidth}{-\centeroffset}
\thispagestyle{empty}
\vspace*{\stretch{1}}
\noindent\hspace*{\centeroffset}\makebox[0pt][l]{\begin{minipage}{\textwidth}
\flushright
{\Huge\bfseries PSBLAS 3.0-beta User's guide
}
\noindent\rule[-1ex]{\textwidth}{5pt}\\[2.5ex]
\hfill\emph{\Large A reference guide for the Parallel Sparse BLAS library}
\end{minipage}}

\vspace{\stretch{1}}
\noindent\hspace*{\centeroffset}\makebox[0pt][l]{\begin{minipage}{\textwidth}
\flushright
{\bfseries 
by Salvatore Filippone\\
and Alfredo Buttari}\\ 
University of Rome ``Tor Vergata''.\\[3ex]
May 15th, 2010.
\end{minipage}}

%\addtolength{\textwidth}{\centeroffset}
\vspace{\stretch{2}}

\cleardoublepage
\begingroup
  \renewcommand*{\thepage}{toc}
  \pagenumbering{roman}   % Roman numbering
  \setcounter{page}{1}    % Abstract start on page ii
  \tableofcontents
\endgroup  

\cleardoublepage

\pagenumbering{arabic}  % Arabic numbering
\setcounter{page}{1}    % Chapters start on page 1

\include{intro}
\include{datastruct}
\include{psbrout}
\include{commrout}
\include{toolsrout}
\include{penv}
\include{error}
\include{util}
\include{precs}
\include{methods}

\cleardoublepage

\begin{thebibliography}{99}

\bibitem{PARA04FOREST}
G.~Bella, S.~Filippone, A.~De Maio and M.~Testa,
{\em A Simulation Model for Forest Fires},
in J.~Dongarra, K.~Madsen, J.~Wasniewski, editors,
Proceedings of PARA~04 Workshop on State of the Art
in Scientific Computing, pp.~546--553, Lecture Notes in Computer Science,
Springer, 2005.
\bibitem{2007d} A. Buttari, D. di Serafino, P. D'Ambra, S. Filippone,\newblock
2LEV-D2P4: a package of high-performance preconditioners,\newblock
Applicable Algebra in Engineering, Communications and Computing, 
Volume 18, Number 3, May, 2007, pp.  223-239
%Published online: 13 February 2007, {\tt http://dx.doi.org/10.1007/s00200-007-0035-z}
%
\bibitem{2007c}  P. D'Ambra, S. Filippone,  D. Di Serafino\newblock
On the Development of PSBLAS-based Parallel Two-level Schwarz Preconditioners
\newblock
Applied Numerical Mathematics, Elsevier Science, 
Volume 57, Issues 11-12, November-December 2007, Pages 1181-1196.
%published online 3 February 2007, {\tt
%  http://dx.doi.org/10.1016/j.apnum.2007.01.006}

\bibitem{BLAS2}
 Dongarra, J. J.,  DuCroz, J.,  Hammarling, S. and Hanson, R.,
An Extended Set of {F}ortran {B}asic {L}inear {A}lgebra {S}ubprograms,
{ACM Trans. Math. Softw.} vol.~{14}, 1--17, 1988.
\bibitem{BLAS3}
  Dongarra, J., DuCroz, J., Hammarling, S. and Duff, I.,
A  Set of level 3 Basic Linear Algebra Subprograms,
{ACM Trans. Math. Softw.} vol.~{16}, 1--17, 1990.
%% \bibitem{DOUGLAS}
%% R.E.~Bank and C.C.~Douglas,
%% {\em SMMP: Sparse Matrix Multiplication Package}, 
%% Advances in Computational Mathematics, 1993, 1, 127-137.
%% (See also {\tt http://www.mgnet.org/~douglas/ccd-codes.html}) 
%
%
%% \bibitem{PARA04}
%% A.~Buttari, P.~D'Ambra, D.~di Serafino and S.~Filippone,
%% {\em Extending PSBLAS to Build Parallel Schwarz Preconditioners},
%% in , J.~Dongarra, K.~Madsen, J.~Wasniewski, editors,
%% Proceedings of PARA~04 Workshop on State of the Art
%% in Scientific Computing, pp.~593--602, Lecture Notes in Computer Science,
%% Springer, 2005.
%
%% \bibitem{CAI_SAAD}
%% X.~C.~Cai and Y.~Saad,
%% {\em Overlapping Domain Decomposition Algorithms for General Sparse Matrices},
%% Numerical Linear Algebra with Applications, 3(3), pp.~221--237, 1996.
%% %
%% \bibitem{CAI_SARKIS}
%% X.C.~Cai and M.~Sarkis,
%% {\em A Restricted Additive Schwarz Preconditioner for General Sparse Linear Systems},
%% SIAM Journal on Scientific Computing, 21(2), pp.~792--797, 1999.
%
%% \bibitem{CAI_WIDLUND}
%% X.C.~Cai and O.~B.~Widlund,
%% {\em Domain Decomposition Algorithms for Indefinite Elliptic Problems},
%% SIAM Journal on Scientific and Statistical Computing, 13(1), pp.~243--258, 1992.
%
%% \bibitem{DD1}
%% T.~Chan and T.~Mathew,
%% {\em Domain Decomposition Algorithms},
%% in A.~Iserles, editor, Acta Numerica 1994, pp.~61--143, 1994.
%% Cambridge University Press.
%% %
%% \bibitem{APNUM06}
%% P.~D'Ambra, D.~di Serafino and S.~Filippone,
%% On the Development of PSBLAS-based Parallel Two-level Schwarz Preconditioners,
%% Applied Numerical Mathematics, to appear, 2007.
%
%% \bibitem{UMFPACK}
%% T.A.~Davis, 
%% {\em Algorithm 832: UMFPACK - an Unsymmetric-pattern Multifrontal
%% Method with a Column Pre-ordering Strategy},
%% ACM Transactions on Mathematical Software, 30, pp.~196--199, 2004.
%% (See also {\tt http://www.cise.ufl.edu/~davis/})
%% %
%% \bibitem{SUPERLU}
%% J.W.~Demmel, S.C.~Eisenstat, J.R.~Gilbert, X.S.~Li and J.W.H.~Liu,
%% A supernodal approach to sparse partial pivoting,
%% SIAM Journal on Matrix Analysis and Applications, 20(3), pp.~720--755, 1999.
%
\bibitem{BLACS}
J.~J.~Dongarra and R.~C.~Whaley,
{\em A User's Guide to the BLACS v.~1.1},
Lapack Working Note 94, Tech.\ Rep.\ UT-CS-95-281, University of
Tennessee, March 1995 (updated May 1997).
%
\bibitem{sblas97}
I.~Duff, M.~Marrone, G.~Radicati and C.~Vittoli,
{\em Level 3 Basic Linear Algebra Subprograms for Sparse Matrices: 
a User Level Interface},
ACM Transactions on Mathematical Software, 23(3), pp.~379--401, 1997.
%
\bibitem{sblas02}
I.~Duff, M.~Heroux and R.~Pozo,
{\em An Overview of the Sparse Basic Linear
Algebra Subprograms: the New Standard from the BLAS Technical Forum},
ACM Transactions on Mathematical Software, 28(2), pp.~239--267, 2002.
\bibitem{PSBLAS}
S.~Filippone and M.~Colajanni, 
{\em PSBLAS: A Library for Parallel Linear Algebra
Computation on Sparse Matrices},
\newblock
ACM Transactions on Mathematical Software, 26(4), pp.~527--550, 2000.
%
\bibitem{KIVA3PSBLAS}
S.~Filippone, P.~D'Ambra, M.~Colajanni,
{\em Using a Parallel Library of Sparse Linear Algebra in a Fluid Dynamics 
Applications Code on Linux Clusters},
in G.~Joubert, A.~Murli, F.~Peters, M.~Vanneschi, editors,
Parallel Computing - Advances \& Current Issues,
pp.~441--448, Imperial College Press, 2002. 
%
\bibitem{METIS}
Karypis, G. and Kumar, V.,
{\em {METIS}: Unstructured Graph Partitioning and Sparse Matrix
  Ordering System}.
Minneapolis, MN 55455: University of Minnesota, Department of
  Computer Science, 1995. 
Internet Address: {\verb|http://www.cs.umn.edu/~karypis|}.
\bibitem{BLAS1}
Lawson, C.,  Hanson, R., Kincaid, D. and Krogh, F.,
   Basic {L}inear {A}lgebra {S}ubprograms for {F}ortran usage,
{ACM Trans. Math. Softw.} vol.~{5}, 38--329, 1979.

\bibitem{machiels}
{Machiels, L. and Deville, M.}
{\em Fortran 90: An entry to object-oriented programming for the solution
  of partial differential equations.}
{ACM Trans. Math. Softw.} vol.~{23}, 32--49.
\bibitem{metcalf}
{Metcalf, M., Reid, J. and Cohen, M.}
{\em Fortran 95/2003 explained.}
{Oxford University Press}, 2004.
%
%% \bibitem{DD2}
%% B.~Smith, P.~Bjorstad and W.~Gropp,
%% {\em Domain Decomposition: Parallel Multilevel Methods for Elliptic
%% Partial Differential Equations},
%% Cambridge University Press, 1996.
%
\bibitem{MPI1}
M.~Snir, S.~Otto, S.~Huss-Lederman, D.~Walker and J.~Dongarra,
{\em MPI: The Complete Reference. Volume 1 - The MPI Core}, second edition,
MIT Press, 1998.
%
\end{thebibliography}

\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: 'userguide'
%%% End: 
